---
title: "Dynastic Impacts on Electoral Outcomes"
output:
  pdf_document: default
subtitle: Replication and Extension of Smith and Martin (2017)
header-includes:
# Create double spacing
- \usepackage{setspace}\doublespacing
# Allow figures and tables to appear next to text
- \usepackage{float}
# Disable automatic captions for tables
- \usepackage[labelformat=empty]{caption}
# Set the paragraph indent and spacing.
- \usepackage{sectsty}
- \setlength{\parindent}{0em}
- \setlength{\parskip}{1em}
# Adjust the font size.
- \usepackage[fontsize=11pt]{scrextend}
---

\begin{flushright}
Jack Schroeder

Gov 1006 Final Paper

April 31, 2019
\end{flushright}

\vspace{10mm}

\begin{abstract}
In this project, I analyze Smith and Martin (2017)'s "Political Dynasties and the Selection of Cabinet Ministers". I begin by replicating Smith and Martin (2017)'s figures and tables. While some of this output cannot be replicated due to missing data or the inability to reproduce in R (the authors used Stata), I find similar results to the authors in what was producible. From there, I extend the results by using their dataset to analyze the gendered impact of two covariates, dynasty and local experience, on winning election. I conclude that there are significant gender-based effects of dynasty and local experience that may help female candidates with these attributes overcome the gender gap in winning elections. 
\end{abstract}
\newpage

## Introduction  

The importance of political dynasties in legislatures cannot be understated. 

Given enough time, many democracies develop political dynasties. Some of these occur at the local level through mayorships and statehouses, others at the national level through executives and appointees. The legislator, locally elected but serving in a national capacity, presents a unique position for dynasties to thrive in. Since they act as the representatives of their homes, they can have outsized voices in certain conversations and, if effective negotiators, can leverage personal relationships into economic gains for their districts. As such, it is vital for these legislators to excel since, in most cases, their constituents vote them out if they fail to adequately provide for their districts. The importance of individual legislators is magnified in parliamentary systems, in which the governing party selects individual legislators to serve in cabinet and run the government.  

In this paper, I begin by introducing Smith and Martin (2017). After reviewing the literature on both gender representation and introducing the reader to the specifics of Ireland's electoral system, I put forward Smith and Martin (2017)'s hypotheses and two of my own for the extension. Then I detail my replication of "Political Dynasties and the Selection of Cabinet Ministers". After that, I focus on two gender-based extensions. The first looks at the potential mitigating factors of dynastic membership in counteracting the gender gap in winning elections. The second analyzes whether local office experience uniquely helps women win election. 

## Literature Review  

### Political Dynasties

Daniel Smith and Shane Martin (2017) analyze the interaction of these political dynasties in cabinet formation. Their goals are threefold: closely survey the electoral advantage legacies hold over nonlegacies, judge whether cabinet legacies - whose predecessors served in cabinet - have an advantage in progressing into cabinet over noncabinet legacies, and dissect the potential mechanisms behind this effect. To accomplish this, the authors work with a candidate-level dataset of Irish politicians encompassing all legislative candidates from 1918-2016 (*n = 11670*), which is described in detail in the "Data" section. They find that legacies indeed hold an electoral advantage over nonlegacies equal to over 35 percentage points, but that this advantage is not statistically different between cabinet and noncabinet legacies. They further that cabinet legacies hold an approximately 8 percentage point advantage over noncabinet legacies in cabinet selection. In proposing potential mechanisms, they focus on an informational advantage held by cabinet legacies and suggest that networking helps explain part of this advantage.  

While Smith and Martin (2017) distance themselves from judging the impacts of dynastic rule, there is ample - but divided - literature on the topic. Using economic data from India, Eapen George and Ponattu (2017) estimate that dynastic rule tends to slow economic growth within each dynastic constituency, worsen the provision of public goods across constituencies, and heighten ethnic polarization among voters. This evidence goes against the common refrain that members of political dynasties are better at legislating because of a greater familiarity with the political system. Indeed, it may be the case that dynasties lead to worse governance. Tusalem and Pe-Aguirre (2013) conclude through their analysis of dynasties in the Philippines that provinces dominated by dynasties tend to spend money less effectively on infrastructure and health than other provinces, while they also have more crime and unemployment. Most strikingly, even though the presence of dynasties tends to include higher levels of congressional earmarks, dynasties spend the money less effectively than their counterparts.  

That said, there is reason to believe dynasties can be normatively beneficial. Lacriox et al (2019) analyze the French Parliament during the initial stages of World War Two and find that members of dynasties were significantly more pro-democratic in their voting records than non-dynasties. However, there were striking disparities between dynasties, leading the authors to conclude that there exist separate types of dynasties, each with their own goals toward coalescing power. While dynasties founded by or filled by members of a pro-democratic party (or non-affiliated members who openly supported a democratic France) tended to defend democratic rights, other dynasties acted no more democratic than non-dynasties.  

### Why Ireland? (and a Review of Electoral Literature) 

Ireland is an interesting case study to examine the impact of mostly exogenous covariates (dynastic status and local experience) on winning election. Its electoral system is classified as a proportional representation-based single transferable vote. Broadly speaking, proportional representation (PR) refers to an electoral system in which different parties gain seats in the legislature at a rate consistent with their vote shares. Proportional representation can happen under a variety of different voting methods, but Ireland uses a single transferable vote (STV). In most PR systems, voters cast their ballots and the seats are apportioned according to the national vote share. Conversely, STV maintains local elections by essentially conducting PR within each district. In Ireland, this goal is accomplished by having multimember districts: districts that send more than one representative to the Dáil (Irish legislature).  

These two factors come together to create a very candidate-based process that I argue better allows us to identify how voters act according to their preferences. In a first-past-the-post system like the United States, there are many conflicting factors like ideology that make it tougher to discern voter preferences. For instance, liberal voters who would prefer to vote for a man rather than a woman faced a challenge in the 2016 Presidential Election because their ideological preferences did not match their gender heuristic. However, in a system where parties nominate multiple candidates or the parties are not as ideologically opposed, voters have more leeway to make decisions based on their own personal preferences.  

While Ireland's major parties were born out of an ideological dispute over secession, they have grown relatively close ideologically in recent decades. Fine Gael (FG) and Fianna Fáil (FF) both have their roots in the debate over the Anglo-Irish Treaty of 1921 that ended the Irish War of Independence. The leaders of what became FG were in favor of this treaty, while members of FF were staunchly opposed to it. Whereas in many countries, ideology determines the first split between parties, the fact that Ireland's parties diverged over a treaty opened the possibility that they would converge in the future. While there exist ideological parties in Ireland, they do not hold the same power FG and FF do, as one of these parties has been in the governing coalition for every Dáil in the post-World War II era.  

Ireland's electoral system may have impacts on equality of gender representation. Reynolds (1999) comments on the variation in gender equality by electoral system. A first-past-the-post structure with single-member districts encourages parties to put forward candidates they feel have majority support, which can disincentivize fielding women or minorities. On the other hand, systems with proportional representation or multimember districts incentivize parties to nominate more diverse slates of candidates to maximize the chances of winning the most seats. In other words, when parties can win multiple seats, they can cater different candidates to different voter bases.  

However, focusing only on the electoral systems ignores the roles of party leaders. Kunovich and Paxton (2005) dig deeper into the gender dynamics at play in this setting. They argue that in proportional systems, greater female leadership on the party level will translate into more female *candidates* in proportional systems, but only in non-proportional systems will female leadership have a direct effect on *successful* candidates. This is because when faced with a potentially sexist electorate, the party primary process in non-proportional, single-member systems has a gatekeeper effect that allows party leaders to circumvent voter preferences by influencing the nomination process to certain candidates' advantage. Paired with ideological differences between parties, the end result is a voter base that seemingly does not have any choice but to vote for a candidate they find distasteful on the basis of race, gender, orientation, religion, etc. This phenomenon provides an alternate pathway for greater gender equality in representation in non-proportional systems, but for the purposes of this project, it highlights that Ireland's electoral systems uniquely and directly expose voter preferences in ways that other systems do not. For this reason, even if a similar candidate dataset existed for the United States, Ireland may still be a useful case.  

## Data

Smith and Martin (2017) use historical election data to compile a unique dataset of all candidates for the Irish legislature from 1918-2016. To account for instability following the independence movement, the authors restrict their sample to 1944-2016. The dataset includes electoral, historical, and demographic information. The electoral information includes the binary result of each election and the vote-share each candidate achieved in their respective district. The historical information includes each candidates’ history within the district: whether they held local office before running, how many times they ran, and how many times they were successful. The demographic information includes age, gender, education level, alma mater, and family information that indicates whether the candidate is a part of a political dynasty. The authors clean the dataset and add new variables like region to create the fixed effects they use in modeling dynastic impacts.  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# I load in three libraries. The first, lfe, allows me to regress using absorbed
# fixed effects (similar to the absorb function in Stata). The second, stargazer,
# lets me create regression output tables. The third is tidyverse, which is useful
# when wrangling with data.

library(lfe)
library(stargazer)
library(tidyverse)

# Smith and Martin leave two data files in the Dataverse. Both of them contain the same
# data. Since I'm more familiar with reading in a csv file versus a dta file (and I
# want to limit the libraries called), I read in their csv data in as csv_data.

csv_data <- read_csv("Smith-Martin-Replication-Data/IRELAND-CANDIDATES.csv")

```

```{r data cleaning, echo=FALSE, cache=TRUE}

# Smith and Martin recode a lot of values before going into their analysis.

csv_data <- csv_data %>% 

# The first mutate is a scalar value of whether a politician is a legacy. What are these
# values? pre_mp is equal to 1 if past family members were elected to the Dail
# (Ireland's) lower house. cablegacy is coded 1 if their direct predecessor served in
# cabinet. All other values on this scale are equal to 0.
  
  mutate(legacyscale = case_when(cablegacy == 1 ~ 2,
                                 pre_mp == 1 ~ 1,
                                 TRUE ~ 0),

# I then add a dynasty variable for my extension. This is a binary equal to 1 if the 
# candidate qualifies as a dynasty.
         
         dynasty = case_when(legacyscale > 0 ~ 1,
                             TRUE ~ 0),
  
# cwins is the number of times (including the current term) the candidate has won
# election to the Dail. est_age is the estimated age of each candidate (if unknown) or
# the actual age (which is found in age). This age is taken from when the candidate
# runs/wins for the first time. Presumably Smith and Martin wanted to see if these
# numbers are still influential on an exponential scale.

         cwins2 = cwins^2,
        est_age2 = est_age^2,
        age2 = age^2,

# Then we have to recode some values already in the dataset into groups. The first is
# a group of estimated ages. The next is recoding educode to new values. educode refers
# to the highest degree received. 1 is primary school, 2 is secondary school, 3 is 
# tertiary, 4 university, and 5 postgraduate. They recode tertiary and university to have
# the same value in educode2.

        agegroup = case_when(est_age > 29 ~ 1,
                             est_age > 39 ~ 2,
                             est_age > 49 ~ 3,
                             est_age > 59 ~ 4,
                             TRUE ~ 0),
        educode2 = case_when(educode == 2 ~ 1,
                             educode == 3 ~ 2,
                             educode == 4 ~ 2,
                             educode == 5 ~ 3,
                             TRUE ~ as.double(educode)),

# offprof is whether the candidate had an "official" profession (which I think refers to
# a senior level). I code that using a case_when.

        offprof = case_when(iscoid < 3 ~ 1,
                            TRUE ~ 0),

# I also found it really helpful to recode legacyscale as the actual name values used in
# graphing (nonlegacy, noncabinet legacy, and cabinet legacy). I assign this to
# legacyname.

        legacyname = case_when(legacyscale == 0 ~ "Nonlegacy",
                               legacyscale == 1 ~ "Noncabinet legacy",
                               legacyscale == 2 ~ "Cabinet legacy"),

# The next recode focuses on the Dail term. There had been 32 Dail terms by 2016, but 
# the current dataset only looks at them as the term number. Since these terms have
# varying lengths, recoding them into years may yield stronger results on legacy.

        dailyear = case_when(dail ==  1 ~ 1918 ,
                             dail ==  2 ~ 1921,
                             dail ==  3 ~ 1922,
                             dail ==  4 ~ 1923,
                             dail ==  5 ~ 1927,
                             dail ==  6  ~ 1927,
                             dail ==  7 ~ 1932,
                             dail ==  8 ~ 1933,
                             dail ==  9 ~ 1937,
                             dail ==  10 ~ 1938,
                             dail ==  11 ~ 1943,
                             dail ==  12 ~ 1944,
                             dail ==  13 ~ 1948,
                             dail ==  14 ~ 1951,
                             dail ==  15 ~ 1954,
                             dail ==  16 ~ 1957,
                             dail ==  17 ~ 1961,
                             dail ==  18 ~ 1965,
                             dail ==  19 ~ 1969,
                             dail ==  20 ~ 1973,
                             dail ==  21 ~ 1977,
                             dail ==  22 ~ 1981,
                             dail ==  23 ~ 1982,
                             dail ==  24 ~ 1982,
                             dail ==  25 ~ 1987,
                             dail ==  26 ~ 1989,
                             dail ==  27 ~ 1992,
                             dail ==  28 ~ 1997,
                             dail ==  29 ~ 2002,
                             dail ==  30 ~ 2007,
                             dail ==  31 ~ 2011,
                             dail ==  32 ~ 2016),

# Another large case_when recode here with assigning districts to regions 
# for Table 7. This was even longer in the original Stata.

        region = case_when(district == "Carlow Kildare" | 
                             district == "Carlow Kilkenny" | 
                             district == "Kildare" | 
                             district == "Kildare North" |
                             district == "Kildare South" ~ "Carlow-Kildare-Kilkenny",
                           district == "Cavan" | 
                             district == "Cavan Monaghan" | 
                             district == "Monaghan" ~ "Cavan Monaghan",
                           district == "Clare" | 
                             district == "Clare Galway South" ~ "Clare-Galway",
                           district == "Cork Borough" | 
                             district == "Cork City" |
                             district == "Cork City North" | 
                             district == "Cork City South" | 
                             district == "Cork East" | 
                             district == "Cork Mid" | 
                             district == "Cork North" | 
                             district == "Cork North Central" |
                             district == "Cork North East" | 
                             district == "Cork North West" | 
                             district == "Cork South" | 
                             district == "Cork South Central" |
                             district == "Cork South East" | 
                             district == "Cork South West" | 
                             district == "Cork West" ~ "Cork",
                           district == "Donegal" | 
                             district == "Donegal East" | 
                             district == "Donegal Leitrim" | 
                             district == "Donegal North East" | 
                             district == "Donegal South West" | 
                             district == "Donegal West" ~ "Donegal",
                           district == "Dublin Artane" | 
                             district == "Dublin Ballyfermot"| 
                             district == "Dublin Cabra" | 
                             district == "Dublin Central" |
                             district == "Dublin Clontarf" | 
                             district == "Dublin County" |
                             district == "Dublin County Mid" | 
                             district == "Dublin County North" | 
                             district == "Dublin County South" | 
                             district == "Dublin County West" | 
                             district == "Dublin Finglas" | 
                             district == "Dublin Mid West" | 
                             district == "Dublin North" | 
                             district == "Dublin North Central" | 
                             district == "Dublin North East" | 
                             district == "Dublin North West" | 
                             district == "Dublin Rathmines" | 
                             district == "Dublin South" | 
                             district == "Dublin South Central" | 
                             district == "Dublin South East" | 
                             district == "Dublin South West" | 
                             district == "Dublin Townships" | 
                             district == "Dublin West" | 
                             district == "Dun Laoghaire" | 
                             district == "Dun Laoghaire Rathdown" ~ "Dublin",
                           district == "Galway East" | 
                             district == "Galway North" | 
                             district == "Galway North East" | 
                             district == "Galway South" | 
                             district == "Galway West" ~ "Clare-Galway",
                           district == "Kerry North" | 
                             district == "Kerry North-West Limerick" | 
                             district == "Kerry South" ~ "Kerry",
                           district == "Laoighis Offaly" | 
                             district == "Leix Offaly" ~ "Laois-Offaly",
                           district == "Limerick" | 
                             district == "Limerick City" | 
                             district == "Limerick County" | 
                             district == "Limerick East" | 
                             district == "Limerick West" ~ "Limerick",
                           district == "Mayo" | 
                             district == "Mayo East" | 
                             district == "Mayo North" | 
                             district == "Mayo South" | 
                             district == "Mayo West" ~ "Mayo",
                           district == "Athlone Longford" | 
                             district == "Longford Westmeath" | 
                             district == "Meath" | 
                             district == "Meath East" | 
                             district == "Meath West" | 
                             district == "Meath Westmeath" | 
                             district == "Westmeath" ~ "Meath-Westmeath",
                           district == "Leitrim" | 
                             district == "Longford Roscommon" | 
                             district == "Roscommon" | 
                             district == "Roscommon Leitrim" | 
                             district == "Roscommon Leitrim South" | 
                             district == "Sligo" | 
                             district == "Sligo Leitrim" | 
                             district == "Sligo Leitrim North" ~
                             "Sligo-Leitrim-Roscommon",
                           district == "Tipperary" | 
                             district == "Tipperary North" | 
                             district == "Tipperary South" ~ "Tipperary",
                           TRUE ~ district),

# Smith and Martin also recode a few partyid values to a new vector named
# partyidsimple. The changes are minor. Christian Centrists are lumped in with
# the Christian Solidarity, Sinn Fein's workers' parties are lumped in with
# the other workers' parties, Independent Fianna Fail and Fine Gael are recoded
# into their larger counterparts, and some smaller parties are recoded into the
# value 30, which contains other minor parties and non-parties.

      partyidsimple = case_when(partyid == 9 ~ 8,
                                partyid == 14 ~ 15,
                                partyid == 11 ~ 1,
                                partyid == 12 ~ 2,
                                partyid == 16 ~ 30,
                                partyid == 18 ~ 30,
                                partyid == 23 ~ 30,
                                partyid == 26 ~ 30,
                                partyid == 16 ~ 30,
                                TRUE ~ as.double(partyid))) %>% 
  
# Lastly, Smith and Martin filter out results from before 1944. This
# is done to focus on the previous 20 Dails.
  
  filter(elecyear > 1943) %>% 

# Another thing needs to be taken care of first. There was an Irish 
# politician named James Dillon. He was an independent associated with
# the Fine Gael party for most of his career. Smith and Martin go to
# great lengths to make sure he is coded as FG throughout the entire
# dataset. This makes enough sense from a cursory glance of his electoral
# history: he was leader of FG from 1959-1965. I'll indulge the authors and
# recode him.

  mutate(party = case_when(name == "Dillon, James" ~ "FG",
                           TRUE ~ party),
         partyid = case_when(name == "Dillon, James" ~ 2,
                             TRUE ~ as.double(partyid)),
         govparty = case_when(name == "Dillon, James" & elecyear == 1948 ~ 1,
                              TRUE ~ as.double(govparty)),
         firstrun = case_when(cruns == 1 ~ 1,
                              TRUE ~ 0)) %>% 

# Smith and Martin combine some variables into new ones. I do the same using
# the unite function.
  
  unite("party_year", c("partyidsimple", "elecyear"), remove=FALSE) %>% 
  unite("dist_year", c("districtid", "elecyear"), remove=FALSE) %>% 
  unite("party_dail", c("partyidsimple", "dail"), remove=FALSE) %>% 
  unite("party_dist", c("partyid", "districtid"), remove=FALSE) %>% 
  unite("party_region", c("partyid", "region"), remove=FALSE) %>% 
  unite("party_dist_dail", c("partyid", "districtid", "dail"), remove=FALSE) %>% 
  unite("party_region_dail", c("partyid" , "region", "dail"), remove=FALSE)

# There are quite a few rejoins necessary here since some new variables are
# summary data (and some of those are conditional on other factors). I create
# new dataframes for them but will rejoin them back to csv_data after they are
# all created. 

# first_age is the initial age of each candidate when they ran for the first
# time.

first_age <- csv_data %>% 
  group_by(pid) %>% 
  mutate(first_age = min(est_age)) %>% 
  group_by(pid) %>% 
  summarize(first_age = min(first_age))

# first_party is the first party of each candidate.

first_party <- csv_data %>% 
  group_by(pid) %>% 
  mutate(first_party = case_when(cruns == 1 ~ party, TRUE ~ "NA")) %>% 
  group_by(pid) %>% 
  summarize(first_party = min(first_party))

# prelocal looks at whether a candidate had local office experience
# before running for the first time.

prelocal <- csv_data %>% 
  group_by(pid) %>% 
  summarize(prelocal = min(local))

# preseanad analyzes whether a candidate served in the Seanad before
# running for the first time.

preseanad <- csv_data %>% 
  group_by(pid) %>% 
  summarize(preseanad = min(seanad))

# prevwins is how many wins the candidate has had at the time of
# the election.

prevwins <- csv_data %>% 
  mutate(prevwins = cwins) %>% 
  group_by(pid) %>% 
  mutate(prevwins = case_when(result == 1 ~ as.double(prevwins)-1,
                                 TRUE ~ as.double(prevwins))) %>% 
  group_by(pid) %>% 
  summarize(prevwins = min(prevwins))

# ever_elected is coded to 1 if the candidate ever won an election.

ever_elected <- csv_data %>% 
  group_by(pid) %>% 
  summarize(max = max(cwins)) %>% 
  mutate(ever_elected = case_when(max > 0 ~ 1,
                                max == 0 ~ 0)) %>% 
  select(pid, ever_elected)

# I rejoin all of this data back to csv_data.

csv_data <- csv_data %>% 
  full_join(., first_age, by = "pid") %>% 
  full_join(., first_party, by = "pid") %>%
  full_join(., prelocal, by = "pid") %>% 
  full_join(., preseanad, by = "pid") %>% 
  full_join(., prevwins, by = "pid") %>%
  full_join(., ever_elected, by = "pid") %>% 
  
# I also create prevwins2, which is prevwins squared.
  
  mutate(prevwins2 = prevwins ^ 2)

# Changing legacyname into a factor and releveling it helps make the 
# graphs look presentable for the figures.

csv_data$legacyname <- fct_relevel(csv_data$legacyname, c("Nonlegacy", "Noncabinet legacy", "Cabinet legacy"))

```

## Replication  

!!! TAKE OUT TALK OF CODING AND R AND PACKAGES!!!

Smith and Martin (2017) use Stata to create the 7 tables and 6 figures in the paper. As a result, my output does not perfectly match their paper cosmetically. That said, the results are mostly the same. It is entirely possible, though, that using `ggplot2` makes the figures look better and that some of the regression coefficients are off on the hundredths digit and beyond.  

There are some tables and figures that could not be replicated. There was no replication code for Tables 1 and 2 in the Stata code. As a result, I did not attempt to replicate this portion of the paper. Table 1 is a list of the cabinets and governing parties in Ireland from 1944-2016. The cabinets, dates in office, and governing parties are not given in the data, although it would theoretically be possible to figure out whether Fianna Fail or Fine Gael had a majority in the Dáil based on which party won more seats in the most recent election. However, the cabinet and Prime Minister would not be able to be determined from this data, so I left it untouched. Table 2 is a Stata summary table of the family relationships and generations among candidates and TDs. While this table is replicable in R, since the code to create it was not included, I decided to focus on replicating the other tables and figures. The figure not included in this replication is Figure 5, which was used to help explain the informational advantage by analyzing several different controls of experience, demographics, and education. This type of coefficient plot is possible in R, but getting the results to directly match the one in the paper was not possible (and would have looked too disjointed to include).  

Those exceptions aside, Smith and Martin (2017)'s results replicate well. There were two major hurdles in replication: translating Stata code and managing multiple graphs. I was able to recreate most of the figures and tables using the `ggplot2` and `stargazer` libraries, respectively. However, the majority of the replication code focused on cleaning the candidate dataset and adding new variables. Using the `tidyverse`, I was able to condense some of the hard-coding relative to the amount used in Stata. The foremost example of this was when the authors added regional data (to create regional fixed effects). In Stata, the authors had to individually assign each district to a region, but by using the `case_when` function, I was able to assign multiple districts to a single region, which cut down the workload by a decent amount. The second hurdle was multiple graphs within the same figure. The majority of the authors' figures were comprised of three bar graphs, mostly reporting summaries of different attributes along the legacy scale. While there exist ways to save multiple graphs within the same figure, I decided it was best to keep each individual call for `ggplot` separate in case I wanted to call one graph and not another in the final paper.  

I will focus on the authors' first figure, along with tables 3 and 5.  

### Figure 1

```{r fig1, echo=FALSE, cache=TRUE}

# Figure 1 is a stacked bar plot looking at the proportion of legacies among
# candidates, elected TDs, TDs in the coalition party, and cabinet ministers.
# To make Figure 1, I had to do a decent amount of data wrangling. This first
# required me to make percentages of legacy status among each of the four 
# politician categories outlined above.

f1_c <- csv_data %>% 
  count(legacyname) %>% 
  mutate(per = n/sum(n),
         position = "Candidates") %>% 
  select(-n)

f1_td <- csv_data %>% 
  filter(result == 1) %>% 
  count(legacyname) %>% 
  mutate(per = n/sum(n),
         position = "TDs") %>% 
  select(-n)

f1_gtd <- csv_data %>% 
  filter(result == 1, govparty == 1) %>% 
  count(legacyname) %>% 
  mutate(per = n/sum(n),
         position = "Government TDs") %>% 
  select(-n)

f1_cm <- csv_data %>% 
  filter(cabappt == 1) %>% 
  count(legacyname) %>% 
  mutate(per = n/sum(n),
         position = "Cabinet Ministers") %>% 
  select(-n)

# From there, I used rbind to create a long dataset. I also
# made position and legacy name into a factor variables that I 
# releveled to make the graph look better.

f1 <- rbind(f1_c, f1_td, f1_gtd, f1_cm)
f1$position <- as.factor(f1$position)
f1$position <- fct_relevel(f1$position, "Candidates", "TDs", "Government TDs", "Cabinet Ministers")
f1$legacyname <- fct_relevel(f1$legacyname, "Cabinet legacy", "Noncabinet legacy",
                             "Nonlegacy")

# From there, I just had to use ggplot with the fill, stat, and
# position attributes correctly selected to show the values on top
# of one another and in the proper order. I titled and labeled 
# appropriately.

f1 <- f1 %>% 
  ggplot(aes(x=reorder(position, -per), y=per, fill=legacyname)) +
  geom_bar(stat="identity", position="fill") +
  xlab("") +
  ylab("Percent") +
  ggtitle("Figure 1. Proportions of Legacy Among Irish Politicians", subtitle = "1944-2016") +
  guides(fill=guide_legend(title="Legacy Type")) +
  labs(caption = "Note: Candidates ran for elections to the Irish Dáil between 1944-2016.")

f1

```


Smith and Martin (2017)'s first figure demonstrates the magnitude of political dynasties in Irish politics. While over 80% of candidates are not legacies, both types of legacies are disproportionately represented among TDs (elected members of the Dáil), TDs in the governing coalition, and cabinet ministers. And, as an impetus for the paper, the reader notices that cabinet legacies are specifically overrepresented among cabinet ministers. This lends credence to the suggestion that cabinet legacies in particular have some sort of informational advantage over noncabinet legacies that results in them getting chosen at a higher rate. Regardless, Figure 1 shows that the overall magnitude of the legacy advantage is much higher in getting elected than in forming the governing coalition or becoming a cabinet minister, as both noncabinet and cabinet legacies comprise about a quarter of TDs, government TDs, and cabinet ministers. While this figure is primarily used to introduce the paper, I think it does a good job of highlighting the different dynamics at play.  


### Table 3  

```{r t3, echo=FALSE, warning=FALSE, cache=TRUE, results='asis'}

# Table 3 measures the electoral advantage of legacies. It uses the
# election result as its left-hand variable. I use felm here because
# Smith and Martin absorb some of their fixed effects (like party-year),
# and regular lm won't let me do that. All of this uses csv_data. I create
# each model.

# Model 1 is simply looking at legacy's impact on winning.

t3_1 <- felm(result ~ as.factor(legacyscale), csv_data)

# Model 2 is legacy's impact on winning, but with party-year fixed effects.

t3_2 <- felm(result ~ as.factor(legacyscale) | party_year, csv_data)

# Model 3 is the same as Model 2 but with district-year fixed effects.

t3_3 <- felm(result ~ as.factor(legacyscale) | dist_year, csv_data)

# Model 4 looks at being female and being a first-time candidate, along with
# party-year fixed effects.

t3_4 <- felm(result ~ as.factor(legacyscale) + female + firstrun | party_year, csv_data)

# Model 5 reproduces Model 4 but with district-year fixed effects.

t3_5 <- felm(result ~ as.factor(legacyscale) + female + firstrun | dist_year, csv_data)

# I display the output using stargazer.

t3 <- stargazer(t3_1, t3_2, t3_4,
          title = "Table 3. The Electoral Advantage of Legacy: Election Result",
          header = FALSE,
          covariate.labels = c("Noncabinet Legacy", "Cabinet Legacy", "Female", "First Run"),
          dep.var.labels = "Election Result",
          omit.stat = "rsq",
          add.lines = list(c("Party-Year Fixed Effects?", "No", "Yes", "Yes")),
          notes = c("Dependent variable is a dummy variable for whether",
                    "the candidate won election. Coefficients are",
                    "estimates from a linear model. Standard errors in",
                    "parentheses."),
          notes.align = "l")

```

Table 3 analyzes the electoral advantage legacies hold over nonlegacies. While this phenomenon is taken for granted at the onset of the paper, Smith and Martin (2017) want to both quantify the effect and make sure that noncabinet and cabinet legacies enjoy the same advantage. If the effects between legacy type are significantly different, it could explain the divergence in cabinet selection by itself. Similar to the authors, I find a significant electoral advantage of legacies but no significant differences between legacy type. I quantify this advantage to be around 35 percentage points, which matches Smith and Martin (2017). This advantage decreases when party-year fixed effects are included, and shrinks even more when female candidates and first-time candidates are incorporated into the model. I leave out the two models incorporating district-year fixed effects instead of party-year fixed effects to save space and not constrict the rest of the table. The results of those models match the magnitude of those in the paper, though, so it appears that district-year fixed effects replicate fairly well.  

The table does deviate from the one published in Smith and Martin (2017). While the first model - without any fixed effects - has the same coefficients, the standard errors are slightly off. This may be due to differences between how R and Stata calculate standard errors. Models 2 and 3 in the replication report slightly different coefficients and standard errors from the corresponding models in the paper. These differences may also be due to slight differences between R and Stata. Regardless of these minor discrepencies, the magnitude and significance of the results remain the same.  

### Table 5

```{r t5, echo=FALSE, warning=FALSE, cache=TRUE, results='asis'}

# Table 5 looks at cabinet appointment as the output variable. It seeks
# to find out whether legacies have an advantage in getting on cabinet.

# Model 1 looks at legacy's impact on cabinet appointment with no effects.

t5_1 <- felm(cabappt ~ as.factor(legacyscale), csv_data)

# Model 2 adds party fixed effects to Model 1.

t5_2 <- felm(cabappt ~ as.factor(legacyscale) | partyidsimple, csv_data)

# Model 3 adds party-dail fixed effects to Model 1 (similar to party-year
# effects, but focused on which government has power).

t5_3 <- felm(cabappt ~ as.factor(legacyscale) | party_dail, csv_data)

# Model 4 adds candidate wins (and candidate wins squared), along with 
# party-dail fixed effects.

t5_4 <- felm(cabappt ~ as.factor(legacyscale) + cwins + cwins2 | party_dail, 
             csv_data)

# Model 5 adds quota share to Model 4.

t5_5 <- felm(cabappt ~ as.factor(legacyscale) + cwins + cwins2 + quotashare | 
               party_dail, csv_data)

# I display the output with stargazer.

t5 <- stargazer(t5_1, t5_3, t5_4, t5_5,
          title = "Table 5. The Legacy Advantage in Cabinet Selection",
          covariate.labels = c("Noncabinet Legacy", "Cabinet Legacy", "Election Wins", "Election Wins Sq.", "Share of Droop Quota"),
          dep.var.labels = "Cabinet Appointment",
          omit.stat = "rsq",
          add.lines = list(c("Party-Year Fixed Effects?", "No", "Yes", "Yes", "Yes")),
          header = FALSE,
          notes = c("Dependent variable is a dummy variable for whether",
                    "the candidate was appointed to cabinet. Coefficients",
                    "are estimates from a linear model. Standard errors in",
                    "parentheses."),
          notes.align = "l")

```

Table 5 looks at the advantage of cabinet legacies over noncabinet legacies in cabinet selection. Once party-year fixed effects and election wins are incorporated into the model, though, noncabinet legacies face a disadvantage in cabinet selection that is significant at the 0.05 level. The mechanism for this is unclear, but it is entirely possible that legacies of backbench legislators are not given the chance to deviate from their dynasty's role or reputation. Being a noncabinet legacy could also signal weaker candidate quality or a worse relationship with party leaders that is tougher for future legacies to break out of. In model 3, which uses party-year fixed effects and includes election wins and election wins squared, the legacy advantage of cabinet legacies can be quantified at 6 percentage points.  

There are a few differences between my output and the paper. First and foremost, my findings appear to underestimate the cabinet advantage by around 2 percentage points. This could be explained by the differing coefficients when party-year fixed effects are used. This is a bit lower than the 8 percentage points Smith and Martin (2017) settle on, but this have something to do with different party-year fixed effects. The authors also use a smaller sample of candidates to construct Table 5, while I use the full dataset from 1944-2016.   

## Extension  

I extend Smith and Martin (2017) in two ways: analyzing the gendered effect of dynasties on winning election and looking at the effect of another potentially gendered covariate, local experience, on winning election.  

### Gendered Effect of Dynasty  

Smith and Martin (2017) note that "legacies of both types are more likely to be women, which suggests that dynasties may be a significant pathway into politics for female candidate in an otherwise male-dominated parliament" (p. 151). This observation inspired me to dig deeper into the gendered effects of being in a political dynasty. Does being in a dynasty help female candidates counteract the gender gap in winning elections?  

To answer this question, I manipulate the Smith and Martin (2017) dataset to include a binary variable, `dynasty`, that is coded 1 if the candidate qualified as a dynasty. I then regress election result on that and the candidate's sex. I end up with three models: one that has no fixed effects, one that uses the party-year fixed effects from Smith and Martin (2017), and one that uses the authors' district-year fixed effects. That output is below in Table E1.  

Model 1 regresses election result on gender, a binary dynasty variable, and the interaction between gender and dynasty. There are no fixed effects in this model. I find a disadvantage of female non-legacy candidates of 18 percentage points, but the interaction variable suggests that female legacies counteract that disadvantage with a positive gender-legacy effect of 12 percentage points, cutting the gender gap to only 6 percentage points. As would be expected with Table 5, the advantage of male legacies is 36 percentage points. All of these covariates are significant at the 0.01 level.  

Model 2 regresses the same variables as Model 1 and includes party-year fixed effects. It again finds significant effects of gender and dynastic membership, but now the interaction between gender and dynasty is not significant at the .1 level. Model 3, which uses district-year fixed effects, has a significant interaction at the 0.1 level that cuts the gender gap by more than half.  

This part of the paper, while an extension on Smith and Martin (2017), is not fully unique. After creating my models, I found that Daniel Smith currently has a working paper studying the same topic with the Irish candidate dataset using similar modeling techniques. As a result, this portion of the extension is also a replication of Folke, Rickne, and Smith (2017). They do not account for fixed effects in their models, which allows them to conclude a significant interaction variable at the 0.01 level (as seen in Model 1), while I can only conclude signficance at the 0.1 level after taking the district-year fixed effects into account.  

The major methodological difference between my analysis and Folke, Rickne, and Smith (2017) is that they restrict their sample to Ireland's three largest parties (Fianna Fáil, Fine Gael, and Labour). They justify this decision because those parties have been consistently nominating candidates in most districts. However, I think the results should still hold without subsetting the data in this fashion because (a) there is still a model that creates party-year fixed effects and (b) since Ireland's electoral system places an emphasis on individual candidates, it should not necessarily matter that a party was consistently nominating in each district.  


```{r extension 1, echo=FALSE, warning=FALSE, results='asis'}

te1_1 <- felm(result ~ female*dynasty, data=csv_data)

te1_2 <- felm(result ~ female*dynasty | party_dail, data=csv_data)

te1_3 <- felm(result ~ female*dynasty | dist_year, data=csv_data)

te1 <- stargazer(te1_1, te1_2, te1_3,
                 title = "Table E1: Gendered Effect of Dynasty",
                 header=FALSE,
                 add.lines = list(c("Fixed Effects?", "No", "Party-Year", "District-Year")),
                 covariate.labels = c("Female",
                                      "Dynasty",
                                      "Female * Dynasty"),
                 dep.var.caption = "Dependent Variable:",
                 dep.var.labels = "Election Result",
          notes = c("Dependent variable is a dummy variable for whether",
                    "the candidate won election. Coefficients are",
                    "estimates from a linear model. Standard errors in",
                    "parentheses."),
          notes.align = "l")
```


### Gendered Effect of Local Experience  

I then explore whether other covariates could have differing effects by gender. Local political experience is of special interest because there seem to be two diverging opinions surrounding its gendered effects.  

The first is pessimistic. Okimoto and Brescoll (2010) observe that female candidates seen as ambitious are punished by voters, while male candidates seen in a similar light are not penalized. Excluding a general "feeling" potential voters could get after meeting a candidate face-to-face or watching them in a debate, local experience seems to be the best signal for ambition available to study. While the overall effect of holding local office is positive for men, the effect for women would be expected to be diminished or even negative if the "ambition hypothesis" holds.  

The second possibility is more optimistic about the effect of local experience on female representation, even though it relies on a sexist electorate. Survey data from Fox (2003) demonstrates that fewer women run for office than men because they are more pessimistic about their qualifications. Additionally, research from Huddy and Terkildsen (1993) suggests that female candidates are held to a higher standard than male candidates in elections. It follows, then, that local experience can both incentivize better female candidates to run and give them the extra qualifications necessary to beat male candidates. In fact, if the assumptions prove true, female candidates should gain more benefit from local experience than male candidates do since the electorate seemingly demands more qualifications from women before voting them into office. As a result, the effect of women holding local office should counteract the gender gap.  

To determine which of these hypotheses most accurately reflect the data, I recreate the models from the first extension and apply them to the interaction between candidate sex and local political experience. Again, I create three models: one without fixed effects, one taking party-year effects into account, and one taking district-year effects into account. As in the first extension, I do not subset the data to only include the major parties. The results of the models are summarized below in Table E2.  

```{r extension 2, echo=FALSE, warning=FALSE, results='asis'}

te2_1 <- felm(result ~ female*local, data=csv_data)

te2_2 <- felm(result ~ female*local | party_dail, data=csv_data)

te2_3 <- felm(result ~ female*local | dist_year, data=csv_data)

te2 <- stargazer(te2_1, te2_2, te2_3,
                 title = "Table E2: Gendered Effect of Local Experience",
                 header=FALSE,
                 add.lines = list(c("Fixed Effects?", "No", "Party-Year", "District-Year")),
                 covariate.labels = c("Female",
                                      "Local Experience",
                                      "Female * Local Experience"),
                 dep.var.caption = "Dependent Variable:",
                 dep.var.labels = "Election Result",
          notes = c("Dependent variable is a dummy variable for whether",
                    "the candidate won election. Coefficients are",
                    "estimates from a linear model. Standard errors in",
                    "parentheses."),
          notes.align = "l")
```

Model 1 regresses election result on candidate gender, local political experience, and the interaction between those variables. There are no fixed effects. The gender gap is estimated to be 24 percentage points, and the benefit to local experience for a male candidate is estimated to be 15 percentage points. The interaction variable, which measures the unique effect of local experience for female candidates, is worth 10 percentage points. This interaction helps female candidates with local experience make up less than half of the gender gap. I find gender and local experience to be significant at the 0.01 level, and the interaction is significant at the 0.05 level.  

Models 2 and 3 both incorporate fixed effects. In model 2, which uses party-year fixed effects, the interaction variable is no longer significant at the 0.1 level, similar to the party-year model in Table E1. However, in model 3, district-year fixed effects yield an interaction variable that is again significant at the 0.05 level. This model estimates that local experience helps female candidates make up two-thirds of the gender gap.  

## Discussion

Smith and Martin (2017)'s results successfully replicate when translated into R. Political legacies indeed hold an electoral advantage over nonlegacies worth over 35 percentage points, and cabinet legacies have around an 8 point advantage over noncabinet legacies in cabinet promotion. The exact mechanism behind this advantage remains unclear and is a topic for future research. I extend Smith and Martin (2017) in two ways. The first analyzes the impact of political dynasties on gender representation. The second looks at another potential covariate, local political experience, and its gender-specific effects. Similar to Folke, Rickne, and Smith (2017), I find that dynastic membership almost entirely counteracts the gender gap in winning elections and that this interaction is significant at the 0.01 level. For local experience, the results are more mixed. While the interaction between gender and local experience is significant at the 0.05 level as a whole and under district-year fixed effects, the relationship is no longer significant when using party-year fixed effects. Even at its peak, this interaction only makes up for half of the gender gap, suggesting that nominating local figures may not be enough to achieve equitable representation. Some suggestions for future research include replicating the paper in Stata. More importantly, however, would be seeing if these results replicate using logistic regression, since election result and cabinet appointment are both binary variables. As a whole, research into other cases besides Ireland would help benefit the literature and further the development of a overarching theory of dynasty and equitable representation.  

\newpage

## Appendix  

Below are the figures and tables included in Smith and Martin (2017) that I choose not to display in the "Replication" portion of the paper.  

### Figures

```{r figdata, echo=FALSE, cache=TRUE}

# A lot of the figures rely on the same subset of data.
# I create that new data here. This data is the csv data but
# only looking at candidates who at one point won election.

figdata <- csv_data %>% 
  filter(ever_elected == 1)

```

```{r fig2, echo=FALSE, cache=TRUE}

# Figure 2 (and 3 and 4) look at attribute data prior to election.
# Unlike Figure 1, they are not stacked bar plots. This makes things
# a bit easier when wrangling data. All I have to do is create the proper
# percentages before calling for ggplot. Keep in mind that in the paper 
# and in this replication, many of these figures are multiple graphs.

f2_local <- figdata %>% 
  filter(!is.na(prelocal)) %>% 
  count(legacyname, prelocal) %>% 
  spread(prelocal, n) %>% 
  mutate(per_local = `1`/(`1`+`0`)) %>% 
  select(legacyname, per_local)

f2_seanad <- figdata %>% 
  filter(!is.na(preseanad)) %>% 
  count(legacyname, preseanad) %>% 
  spread(preseanad, n) %>% 
  mutate(per_seanad = `1`/(`1`+`0`)) %>% 
  select(legacyname, per_seanad)

f2_offprof <- figdata %>% 
  filter(!is.na(offprof)) %>% 
  count(legacyname, offprof) %>% 
  spread(offprof, n) %>% 
  mutate(per_offprof = `1`/(`1`+`0`)) %>% 
  select(legacyname, per_offprof)

# I call ggplot three times and assign each plot to hide until needed.

f2_1 <- ggplot(f2_local, aes(x=legacyname, y=per_local, fill=legacyname)) + 
  geom_bar(stat="identity") + 
  xlab("") +
  ylab("") +
  ggtitle("Figure 2. Pre-Electoral Experience (Local)", subtitle = "Sorted by Legacy Status") +
  guides(fill=guide_legend(title="Legacy Type"))

f2_2 <- ggplot(f2_seanad, aes(x=legacyname, y=per_seanad, fill=legacyname)) + 
  geom_bar(stat="identity") + 
  xlab("") +
  ylab("") +
  ggtitle("Figure 2. Pre-Electoral Experience (Seanad)", subtitle = "Sorted by Legacy Status") +
  guides(fill=guide_legend(title="Legacy Type"))

f2_3 <- ggplot(f2_offprof, aes(x=legacyname, y=per_offprof, fill=legacyname)) + 
  geom_bar(stat="identity") + 
  xlab("") +
  ylab("") +
  ggtitle("Figure 2. Pre-Electoral Experience (Professional)", subtitle = "Sorted by Legacy Status") +
  guides(fill=guide_legend(title="Legacy Type"))

# I call for each plot in the appendix.

f2_1
f2_2
f2_3

```

```{r fig3, echo=FALSE, cache=TRUE}

# Whereas Figure 2 looked at experience data, Figure 3 looks at demographic
# data. I do the same data wrangling process as for Figure 2.

f3_female <- figdata %>% 
  filter(!is.na(female)) %>% 
  count(legacyname, female) %>% 
  spread(female, n) %>% 
  mutate(per_female = `1`/(`1`+`0`)) %>% 
  select(legacyname, per_female)

f3_first_age <- figdata %>% 
  filter(!is.na(first_age)) %>% 
  group_by(legacyname) %>% 
  summarize(avg_first_age = mean(first_age)) %>% 
  select(legacyname, avg_first_age)

f3_localborn <- figdata %>% 
  filter(!is.na(localborn)) %>% 
  count(legacyname, localborn) %>% 
  spread(localborn, n) %>% 
  mutate(per_localborn = `1`/(`1`+`0`)) %>% 
  select(legacyname, per_localborn)

# Then I assign each plot to f3_1, f3_2, and f3_3. This lets me
# hide the output until needed.

f3_1 <- ggplot(f3_female, aes(x=legacyname, y=per_female, fill=legacyname)) + 
  geom_bar(stat="identity") + 
  xlab("") +
  ylab("") +
  ggtitle("Figure 3. Pre-Electoral Demographics (Female)", subtitle = "Sorted by Legacy Status") +
  guides(fill=guide_legend(title="Legacy Type"))

f3_2 <- ggplot(f3_first_age, aes(x=legacyname, y=avg_first_age, fill=legacyname)) + 
  geom_bar(stat="identity") + 
  xlab("") +
  ylab("") +
  ggtitle("Figure 3. Pre-Electoral Demographics (Age at First Election)", subtitle = "Sorted by Legacy Status") +
  guides(fill=guide_legend(title="Legacy Type"))

f3_3 <- ggplot(f3_localborn, aes(x=legacyname, y=per_localborn, fill=legacyname)) + 
  geom_bar(stat="identity") + 
  xlab("") +
  ylab("") +
  ggtitle("Figure 3. Pre-Electoral Demographics (Local Born)", subtitle = "Sorted by Legacy Status") +
  guides(fill=guide_legend(title="Legacy Type"))

# I call for each figure now that this chunk is in the appendix.

f3_1
f3_2
f3_3

```

```{r fig4, echo=FALSE, cache=TRUE}

# Figure 4 looks at the same pre-electoral attribute data, but focusing on
# education. I do the same commands to data wrangle.

f4_postsec <- figdata %>% 
  filter(!is.na(educode2)) %>% 
  count(legacyname, educode2) %>% 
  spread(educode2, n) %>% 
  mutate(per_postsec = `2`/(`1`+`2`+`3`)) %>% 
  select(legacyname, per_postsec)

f4_postgrad <- figdata %>% 
  filter(!is.na(educode2)) %>% 
  count(legacyname, educode2) %>% 
  spread(educode2, n) %>% 
  mutate(per_postgrad = `3`/(`1`+`2`+`3`)) %>% 
  select(legacyname, per_postgrad)

f4_ucd <- figdata %>% 
  filter(!is.na(ucd)) %>% 
  count(legacyname, ucd) %>% 
  spread(ucd, n) %>% 
  mutate(per_ucd = `1`/(`1`+`0`)) %>% 
  select(legacyname, per_ucd)

f4_feeschool <- figdata %>% 
  filter(!is.na(feeschool)) %>% 
  count(legacyname, feeschool) %>% 
  spread(feeschool, n) %>% 
  mutate(per_feeschool = `1`/(`1`+`0`)) %>% 
  select(legacyname, per_feeschool)

# I create four ggplots and assign them in case I want the output to be
# hidden.

f4_1 <- ggplot(f4_postsec, aes(x=legacyname, y=per_postsec, fill=legacyname)) + 
  geom_bar(stat="identity") + 
  xlab("") +
  ylab("") +
  ggtitle("Figure 4. Pre-Electoral Education (Postsecondary Education)", subtitle = "Sorted by Legacy Status") +
  guides(fill=guide_legend(title="Legacy Type"))

f4_2 <- ggplot(f4_postgrad, aes(x=legacyname, y=per_postgrad, fill=legacyname)) + 
  geom_bar(stat="identity") + 
  xlab("") +
  ylab("") +
  ggtitle("Figure 4. Pre-Electoral Education (Postgraduate Degree)", subtitle = "Sorted by Legacy Status") +
  guides(fill=guide_legend(title="Legacy Type"))

f4_3 <- ggplot(f4_ucd, aes(x=legacyname, y=per_ucd, fill=legacyname)) + 
  geom_bar(stat="identity") + 
  xlab("") +
  ylab("") +
  ggtitle("Figure 4. Pre-Electoral Education (UCD)", subtitle = "Sorted by Legacy Status") +
  guides(fill=guide_legend(title="Legacy Type"))

f4_4 <- ggplot(f4_feeschool, aes(x=legacyname, y=per_feeschool, fill=legacyname)) + 
  geom_bar(stat="identity") + 
  xlab("") +
  ylab("") +
  ggtitle("Figure 4. Pre-Electoral Education (Fee School)", subtitle = "Sorted by Legacy Status") +
  guides(fill=guide_legend(title="Legacy Type"))

# I call for each figure now that it is located in the appendix.

f4_1
f4_2
f4_3
f4_4

```

```{r fig6, echo=FALSE, cache=TRUE}

# Figure 6 contrasts cabinet and noncabinet legacies through legacy
# attributes (generation number, sharing the same name/district as
# the predecessor in the dynasty). Generation is shown as the number,
# while same name and same district are shown in percentage form.

fig6data <- figdata %>% 
  filter(pre_mp == 1,
         legacyscale != 0)

f6_generation <- fig6data %>% 
  filter(!is.na(generation)) %>% 
  group_by(legacyname) %>% 
  summarize(avg_generation = mean(generation)) %>% 
  select(legacyname, avg_generation)

f6_samename <- fig6data %>% 
  filter(!is.na(samename)) %>% 
  count(legacyname, samename) %>% 
  spread(samename, n) %>% 
  mutate(per_samename = `1`/(`1`+`0`)) %>% 
  select(legacyname, per_samename)

f6_samedistrict <- fig6data %>% 
  filter(!is.na(samedistrict)) %>% 
  count(legacyname, samedistrict) %>% 
  spread(samedistrict, n) %>% 
  mutate(per_samedistrict = `1`/(`1`+`0`)) %>% 
  select(legacyname, per_samedistrict)

# I assign three ggplots to hide the output until needed.

f6_1 <- ggplot(f6_generation, aes(x=legacyname, y=avg_generation, fill=legacyname)) + 
  geom_bar(stat="identity") + 
  xlab("") +
  ylab("") +
  ggtitle("Figure 6. Strength of the Dynasty (Generation)", subtitle = "Sorted by Legacy Status") +
  guides(fill=guide_legend(title="Legacy Type"))

f6_2 <- ggplot(f6_samename, aes(x=legacyname, y=per_samename, fill=legacyname)) + 
  geom_bar(stat="identity") + 
  xlab("") +
  ylab("") +
  ggtitle("Figure 6. Strength of the Dynasty (Same Name)", subtitle = "Sorted by Legacy Status") +
  guides(fill=guide_legend(title="Legacy Type"))

f6_3 <- ggplot(f6_samedistrict, aes(x=legacyname, y=per_samedistrict, fill=legacyname)) + 
  geom_bar(stat="identity") + 
  xlab("") +
  ylab("") +
  ggtitle("Figure 6. Strength of the Dynasty (Same District)", subtitle = "Sorted by Legacy Status") +
  guides(fill=guide_legend(title="Legacy Type"))

# I call for each figure in the appendix.

f6_1
f6_2
f6_3

```

\newpage

### Tables

```{r t4, echo=FALSE, warning=FALSE, cache=TRUE, results='asis'}

# Table 4 looks at the electoral advantage of legacy, but with quota share
# as the measured output variable. quotashare is the proportion of the Droop
# Quota (used in multimember districts to determine who wins) met by the 
# candidate's first preference votes.

# Model 1 is simply legacy's impact on quota achieved.

t4_1 <- felm(quotashare ~ as.factor(legacyscale), csv_data)

# Model 2 is similar to Model 1 but with party-year fixed effects.

t4_2 <- felm(quotashare ~ as.factor(legacyscale) | party_year, csv_data)

# Model 3 is the same as Model 1 but with district-year fixed effects.

t4_3 <- felm(quotashare ~ as.factor(legacyscale) | dist_year, csv_data)

# Model 4 adds being female and being a first-time candidate to Model 2.

t4_4 <- felm(quotashare ~ as.factor(legacyscale) + female + firstrun | party_year, csv_data)

# Model 5 is the same as Model 4, but with district-year fixed effects.

t4_5 <- felm(quotashare ~ as.factor(legacyscale) + female + firstrun | dist_year, csv_data)

# I use stargazer to generate the table. To save space, I do not report
# the first model that does not include any fixed effects.

t4 <- stargazer(t4_2, t4_3, t4_4, t4_5,
          title = "Table 4. The Electoral Advantage of Legacy: Share of Quota",
          header = FALSE,
          covariate.labels = c("Noncabinet Legacy", "Cabinet Legacy", "Female", "First-time Candidate"),
          dep.var.labels = "Share of Quota",
          omit.stat = "rsq",
          add.lines = list(c("Party-Year Fixed Effects?", "Yes", "No", "Yes", "No"), c("District-Year FE?", "No", "Yes", "No", "Yes")),
          notes = c("Dependent variable is the proportion of the electoral quota reached", "by the candidate with his or her first preference votes. Coefficients are", "estimates from a linear model. Standard errors in parentheses."),
          notes.align = "l")

```

```{r t6, echo=FALSE, warning=FALSE, cache=TRUE, results='asis'}

# Table 6 looks at what makes dynasties strong. The output variable is still
# cabinet appointment.

# Model 1 looks at the impact of legacy type, candidate wins, candidate wins squared,
# and which generation in the legacy the candidate is on cabinet appointment. It
# also has party-dail fixed effects. The data is subsetted to legacies.

t6_1 <- felm(cabappt ~ as.factor(legacyscale) + cwins + cwins2 + generation | 
               party_dail, subset(csv_data, pre_mp == 1))

# Model 2 is the same as Model 1 but uses whether the candidate has the same name
# as the dynasty rather than generation.

t6_2 <- felm(cabappt ~ as.factor(legacyscale) + cwins + cwins2 + samename | 
               party_dail, subset(csv_data, pre_mp == 1))

# Model 3 looks at whether the candidate is from the same district as the dynasty
# rather than the same name.

t6_3 <- felm(cabappt ~ as.factor(legacyscale) + cwins + cwins2 + samedistrict |
               party_dail, subset(csv_data, pre_mp == 1))

# I display the output with stargazer.

t6 <- stargazer(t6_1, t6_2, t6_3,
          title = "Table 6. Unpacking the Informational Advantage: Strength of the Dynasty?",
          header = FALSE,
          covariate.labels = c("Noncabinet Legacy", "Cabinet Legacy", "Candidate Wins", "Candidate Wins Squared", "Generation Number", "Same Name?", "Same District?"),
          dep.var.labels = "Cabinet Appointment",
          omit.stat = "rsq",
          add.lines = list(c("Party-Year Fixed Effects?", "Yes", "Yes", "Yes")),
          notes = c("Dependent variable is a dummy variable for whether the candidate was", "appointed to cabinet. Coefficients are estimates from a linear model.", "Standard errors in parentheses."),
          notes.align = "l")

```

```{r t7, echo=FALSE, warning=FALSE, cache=TRUE, results='asis'}

# All of the region hard-coding comes to fruition in Table 7, which
# analyzes whether region has an effect on the impact of legacy. Cabinet 
# appointment is still the output variable.

# Model 1 looks at the impat of legacy on cabinet appointment, with party-region
# fixed effects.

t7_1 <- felm(cabappt ~ as.factor(legacyscale) | party_region_dail, csv_data)

# Model 2 looks adds candidate wins and candidate wins squared to Model 1.

t7_2 <- felm(cabappt ~ as.factor(legacyscale) + cwins + cwins2 | 
               party_region_dail, csv_data)

# I display the output with stargazer.

t7 <- stargazer(t7_1, t7_2,
          title = "Table 7. Unpacking the Informational Advantage: Party Strongholds?",
          header = FALSE,
          covariate.labels = c("Noncabinet Legacy", "Cabinet Legacy", "Candidate Wins", "Candidate Wins Squared"),
          dep.var.labels = "Cabinet Appointment",
          omit.stat = "rsq",
          add.lines = list(c("Party-Region-Year Fixed Effects?", "Yes", "Yes")),
          notes = c("Dependent variable is a dummy variable for whether the candidate was", "appointed to cabinet. Coefficients are estimates from a linear model.", "Standard errors in parentheses."),
          notes.align = "l")

```

\newpage

## References  

Eapen George, S., and Ponattu, D. (2017). Understanding the economic impacts of political dynasties: Evidence from India. *Unviersity of Mannheim*. Retrieved from tufts.edu

Folke, O., Rickne, J., and Smith, D. (2017). Gender and dynastic political recruitment. *Research Institute of Industrial Economics*. Retrieved from ifn.se

Fox, R. (2003). Gender, political ambition, and the decision not to run for office. Union College. Retrieved from cawp.rutgers.edu

Hlavac, M. (2018). stargazer: Well-formatted regression and summary statistics tables. R package version 5.2.2. Retrieved from CRAN.R-project.org

Huddy, L., and Terkildsen, N. (1993). The consequences of gender stereotypes for women candidates at different levels and types of office. Political Research Quarterly 46(3). pp. 503-525.

Kunovich, S., and Paxton, P. (2005). Pathways to power: The role of political parties in women’s national political representation. American Journal of Sociology 111(2). pp. 505-52

Lacroix, J., et al. (2019). A positive effect of political dynasties: The case of France's 1940 enabling act. *Université libre de Bruxelles*. Retrieved from aeaweb.org

Okimoto, T., and Brescoll, V. (2010). The price of power: Power seeking and backlash against female politicians. Personality and Social Psychology Bulletin 36(7). pp. 923-36.

Reynolds, A. (1999). Women in the legislatures and executives of the world: Knocking at the highest glass ceiling. World Politics 51(4). pp. 547-72.

Smith, D., and Martin, S. (2017). Political dynasties and the selection of cabinet ministers. *Legislative Studies Quarterly 42*(1). Retrieved from wiley.com

Smith, D., and Martin, S. (2017). Replication data for: Political dynasties and the selection of cabinet ministers. *Harvard Dataverse*. Retrieved from dataverse.harvard.edu

Tusalem, R., and Pe-Aguirre, J. (2013). The effect of political dynasties on effective democratic governance: Evidence from the Philippines. *Asian Politics & Policy 5*(3). Retrieved from wiley.com